\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\title{
Anti-Society and its Malcontents \\
\large Exposing the Marriage of Marxism and Anti-Society}
\author{Salvador Guzm\'an Jr.}
\date{July 17, 2023}

\begin{document}

\maketitle
\pagebreak

\begin{abstract}
    The viable success of the Marxist political grievance program will demand the attention of researchers for generations.
    How a small cabal of disaffected Marxist intellectuals were able to apply their praxis is of great interests.
    Not only that, they were able to hide their complicity in the destruction of the West by using the very institutions they sought to destroy.
    This paper will attempt to explain how Marxists were able to tap into a thick vein of resentment in the anti-society and use their grievances for political currency.
    As a testament to how successful they were, not only did they bury their tracks but also cement their power among the elites and their respective institutions.
    And now any attempt to extricate the Marxist artifacts from society is greeted with an allergic immuno-response by society.
    Thus, has the apex parasite of Marxism supplanted the host.

\end{abstract}
\pagebreak
\tableofcontents
\pagebreak

\section{Introduction}
\subsection{Marxism as a Political Grievance Program}
\subsection{The Anti-Society}

\section{The Marriage of Marxism and Anti-Society}
\subsection{The Marriage of Marxism and Anti-Society in the Academy}
\subsection{The Marriage of Marxism and Anti-Society in the Media}
\subsection{The Marriage of Marxism and Anti-Society in the Government}
\subsection{The Marriage of Marxism and Anti-Society in the Corporations}
\subsection{The Marriage of Marxism and Anti-Society in the Church}

\section{Marxism}
\subsection{Marxism as Formal Historical Revisionism}
\subsection{Marxism as Symbolic and Verbal Manipulation}
\subsection{Marxism as a Political Grievance Program}
\subsection{Marxism as Intellectual Capture}

\section{Anti-Society}
\subsection{History of the Anti-Society}
\subsection{Prognosis of the Anti-Society}
\subsection{Permanence of the Anti-Society}
\subsection{Pandering to the Anti-Society}

\section{Viability as a Political Program}
\subsection{Success as a Democratic Political Machine}
\subsection{Success as an Outlet of Resentment}
\subsection{Success in Capture of Elites}
\subsection{Success in Capture of Institutions}
\subsection{Success as Program for Prosperity}

\section{Summary}

\subsection{Causes of the Managerial Class}
\begin{enumerate}
    \item ...
\end{enumerate}

\section{Suggested Points of Departure for Future Research}

\end{document}
