% Created 2021-11-22 Mon 11:31
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Salvador Guzman}
\date{\textit{<2021-11-22 Mon>}}
\title{Truth as Process}
\hypersetup{
 pdfauthor={Salvador Guzman},
 pdftitle={Truth as Process},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.0.50 (Org mode 9.5)},
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Introduction}
\label{sec:orge66d11b}

The Halting Problem and its constituent pedagogical discourse circumscribing
it always has impressed me with its oddity. This peculiar problem, I would
introspect in private, has availed itself lavishly to the contemplative spirit
of the human imagination and very much ensconced notions of computation for
our age. Through whatever inventive machinations it could afford, the broad
outline of this logical exercise in futility had found purchase in the minds
of many.

That this phenomena could be explained perhaps by the eagerness of computer
scientists to have under their purview a body of literature rivaling that of
more established intellectual traditions shines brightly for me. The zealotry
in which a nascent school of thought possesses can of course be explained very
much in this way without betraying any elucidating penetrative insight into
the matter that animates this discussion in the first place of course. Should
this explanation prevail, they can be forgiven for their overzealous efforts.
No one is immune from the lofty ambitions that one inherits when commencing an
endeavor of intellectual character. Moreover, doubly can they be forgiven when
their undertaking is haunted by the charismatic bravado that posterity insists
on oppressively bequeathing us.

Truth be had, however, lest those traditions haughtily gesture beyond their
worth, they suffer a similar fate. Not of course in their evocative sense of
eagerness, as time for theirs has come and pass to reap them. No, no; what I
mean to point out, with all this meandering word mincing is that mundane ideas
are granted stature beyond what should be afforded in all sensibility to
meager modicums of thought.

\section{The Halting Problem Proper}
\label{sec:org6782221}
So what is the problem in question that animates this article to be written?
The Halting Problem, as described in my own terms, is often rendered as the
proposition that is it impossible to design or engineer an algorithm, using
whatever matriculation you have at your disposal, whether some arbitrarily
given process (read: algorithm) will terminate.

Substantive to this problem is the asymmetric exhaustion associated with the
two possibilities for the process in question. Either the process exits
normally and subsequently allows the algorithm to determine that the process
halted or the process never halts. Note that the algorithm and the process
both are assumed to run on the same thread, e.g. execution context, and must
therefore trade off execution.

If the process halts, it permits the algorithm the capacity to reason about
the freshly terminated process and conclude that it has ended. However, the
difficulty comes in the non-terminating case. Since execution context is
shared, the process executing starves the algorithm of the ability not just to
run, but to reason. Thusly, the algorithm never is permitted to conclude one
way or another.

Approximately, this resembles the dilemma. I do not wish to rehash the minutia
here. Let it be said there exist many online resources that can do the problem
justice. My purpose here is exposition and only do I weakly desire to capture
the problem in its full scope.

\section{Deconstructing a Problem}
\label{sec:orgfbf698d}
More paramount that I capture the problem faithfully, the general contours of
the problem are what motivated me to write this article. This problem is not
unique in investiture to the lapse of logical rigor in satisfying some
arbitrarily given criteria. Men are creatures of innovation as much as they
are of habit and on circumstance often haunted by tedium. Often their ravenous
analytical ability is animus enough to bleed their contemporary tools of all

\subsection{Paradox if you want it}
\label{sec:org9b143c0}
What I belabor to say, with all matter of pomp and prose, is that the problem
is no problem at all. What the Halting Problem, and other rigorous
intellectual pursuits share, is that their inabilities to whittle away at
purported intractable propositions is by design. Granted, subconscious or
otherwise beholding to unconscious passions but intentional nonetheless.

What always struck me as queer, whenever mathematicians (yes, they are the
other guilty party I alluded to in the past) insist on the injurious and
injudicious leveraging of the word paradox. I do labor as far as to permit
that one man's paradox is relative to each and everyone. Nay; using the most
stringent adherence to the definitions espoused wherein a paradox is
concocted, one can easily arrive at any paradox proper. That is not in
question and the character of the intellectually curious I do not which to
mar.

However, still permitted and what still persists with the tenacity that
arrived at paradox in the first place is the desire to faithfully set the
scene. What scene? Well, that mathematics and all of its accompanying syntax
and notation are man-made, not God-given; that the tools are expressions and
manifestations of human intellect; that these intellectual exercises impress
more of the authors' peculiarities than of the material on which they are
excercised; and finally that any expressions of ineffectual treatment of some
subject or other by these authors articulates more a futility of particular
imagination rather than a bulwark against the intellectual treatment in the
first place.

That is all.

\subsection{Paradox, a choice?}
\label{sec:org53dcf3e}

What permits this conclusion, that paradoxes encountered amid the exercise of
reason are more children of circumstance and temperament of the author than of
some conclusive global statement on the nature of logic itself, is no
grandiose overture. It is the simple return to vision that these are tools.
Intellectual or otherwise; just tools. The constructions we use to wander our
way through the hinterlands of logical consequence are no more objective, no
more perfect, no more Godly, than we are. You would no more engage in the
sacrilegious apotheosis of a simple hammer; wherefore then cometh your faith?

\section{Plato's Revenge}
\label{sec:orga48764c}

If you would afford me a slight digression, I would like to speculate at
length the source of this tool-worship. The name Plato should be no stranger
to you. A great man of great import. What suffices for the subsequent
discussion is that the man possessed a opinionated understanding of
mathematics and its place in our universe.

Plato envisioned that mathematical entities, whether geometric figures or
numbers or proofs, were endowed with an existence that was difficult to
differentiate from the nominal sense of the word as we know of it. The
eponymous platonic solids themselves existed in a divinely inspired realm of
which we have scant knowledge of. Obviously, the prima facie situation is that
we have knowledge enough to know of this divine realm and the constituent
mathematical entities.

It always striked me as odd that one would need to posit the existence of a
whole inaccessible just to permit us the luxury of our mathematical fiction.
Regardless, what is paramount here is the fatal entanglement of beauty and
perfection that Plato assigned to mathematics. There could be little talk of
math without invoking, even indirectly of its capacity to be consumed
aesthetically as well.

Numbers are perfect. Solids are perfect and pristine. And they all exist in
some celestial realm. And we, the unfortunate residents of this miserable
joyless world, can but ruminate on our fall from grace. Humans have only
access to impure analogues to the perfect entities which can only guide
speculation towards the more heavenly realm.

This is Plato. This is his revenge. That we miserable creatures of minor fame
and important and can only lust after perfection, the culmination of
aesthetics, and never adequately indulge our appetite for godliness. This is
his venomous tonic that humanity has only recently braved the effort to
overthrow.

\section{Vindictive Consequences}
\label{sec:org68d29ac}

Given Plato, what is entailed? As aforementioned, worshiping our tools of
logic is one of those consequences. That these tools, sculpted with precision
and rigor, demands a captivated audience and an awed user. What follows from
Plato is nothing less than tool worship. The pious fever dream that devoured
us for nigh two millennia is that history has bequeathed to us numbers,
solids, equations, surfaces; meticulous crafted by better men than us, men
more deserving and god-like. We, the pathetic creatures that the contemporary
modern age contains, should have sense enough of how unworthy we are to
possess these tools. We do not deserve to behold these treasures, let alone
harbor manic desires to transmogrify them for our provincial inventions. Now
that we have sinned against God and coveted these gifts, preserve them for the
next age. And God damn those who fail in this duty.

\section{A Curse Elided}
\label{sec:org1287aea}

That is the curse. History has inherited us these gifts and we strive only in
standing in awe of these creations.

Avoiding the cult-like status that Platonism requires, it simply fails as a
pragmatic paradigm. Tools are tools. As tautological as it sounds, tools have
authors and authors are always of material flesh. They are designed to improve
our lot in life and the authors are no more Godly than we are. Thus, what is
permitted by the tacit admission of tool creation is the ability to create and
modify the very same tools to our liking.

That is what is meant that paradoxes are optional. It is not that they can
always be avoided but rather the emphasis is on their capacity to transpire
being contingent on tools.

\section{Logic: Nothing but a Game}
\label{sec:org8fb6286}

In reasoning about system of intellectual importance, it is helpful to liken
the subject to something more familiar and less exotic. In my case, games are
very simple to understand. They are simple in that they contain rules that are
enforced but ultimately negotiable. What follows from these rules controls the
resulting experience had. Logic is the same way.

Logic is no different way in that its judicious exercise contains rules that
are set before any logical consequences can be had. The axioms are ultimately
negotiable as well.

With this admission, the chief question that should occupy your mind is then
what is the primary concern of logical deduction or induction when the
definitions are fluid. That concern is speculation beyond what I am occupied
with. What should suffice for now is that whatever the motivation is, those
who play games may perchance be intimate to some fragment of wisdom in that
respect.

\section{What is Meant by Paradox in Common Parlance}
\label{sec:org15bb422}

Constituting the semantic interpretation of paradox, then, in mathematical
literature is a more mundane, boring and dry definition. It is meant that
given some finite set of axioms, some formal sentence composed in a scaffold
manner from them stubbornly refuses to permit an exhaustive and conclusive
resolution in regard to its truth value. This is because the rogue sentence
villainously commits to evade logical exhaustion by the auspices granted by
those same axioms. Of course, it is agnostic on the matter on whether or not
some modification of axiomatic origin would allow a concise logical
denouement.

\section{Due Diligence}
\label{sec:org9735a11}

Yet this simple fact is presented with the same pious resolve that one voices
a belief in a deity. Theistic discourse is not resented by this author at all.
What I regard with derision is the ambiguity that tolerates talking of God and
mathematics in the same breath. Speak of God in the firmness of God and speak
of mathematics in the firmness of mathematics.

If mathematics and more chiefly paradoxes were presented in the spirit of
human creations to be tampered with, I imagine more progress would be had
since it would not require a rebellious animus to commit sin against God to
progress forward. Lowering the threshold to less sacrilegious means would be a
boom to development of the mathematical and logical arts since they would
possess more a material character that invites contribution.

\section{Permitting a Solution to the Halting Problem}
\label{sec:org9c58b1f}

Now that all the lucid speculation is finished, I can proceed to brief outline
of what I would consider a modest but satisfactory solution to the halting
problem. A simple solution for the halting problem is possible if one permits
the malleability of the topology of the solution. Instead of a single moment
where the algorithm emits a yes or not, the concept of truth is extended to a
process.

Thus, a simple sketch of my solution is as follows. Each list item occurs
chronologically. The algorithms is executed twice and emits two opposite
results. The process in question runs in between these two calls.

\begin{enumerate}
\item Algorithm assumes that the process will not halt, outputting no
\item Process is ran
\item If this step is reached, then process must have exited and algorithm outputs a yes
\end{enumerate}

In the case that the process does not halt, the initial answer is tantamount
to a conclusive and definitive answer on the matter. However, should the
process actually halt, the initial answer will of course be incorrect. This
should not be problem in atomic conceptions of this construction. Assuming one
allows it, there are obviously available versions of this construction that
posits the existence of a small time gap between each step, infinitesimally
small or otherwise, would burden the entire exercise with a spurious assertion
for the duration of the time gap between steps.

\section{What Exactly is Supplicated}
\label{sec:orgbaadb6e}

The central position of this attempted position is that the topology of the
solution space should match that of the problem. To this observer, it is not
judicious to stoically endure the hardship demanded by those seeking a point
answer to a line problem. In short, the problem has the topology of a line
since execution proceeds in a linear fashion yet a single atomic point is
demanded. There is nothing brave about handicapping oneself in search of a
solution. Even in the case that brevity is preferred, a characteristic of a
more parsimonious approach should not wantonly burden the solution-provider
with unnecessary constraints.

Thus, the supplication asks fairness in dimensions. That the topology of the
problem match that of the solution is prime concern. There is no reason for
ask for a crippled solution, specially when pragmatically-inclined in the
first place. This rough solution that I offered is better than no solution.

\section{More on Truth as Process}
\label{sec:org417135b}
More important than the attempted amelioration of the halting problem is the
idea that truth can be conferred on the basis of a process. If one requires
truth, it can be given on a basis that tolerates deviation from true veracity
as long as the deviation is within some agreed degree. One thinks of
probability theory and statistics which has the idea of a confidence level.
There is no reason that truth cannot function on a more loose footing to allow
for more flexibility.

In distributed systems in computing, there is a well-known theorem called the
CAP theorem that dictates the trade-off inherent in a distributed domain. In
such a setting, truth as a process that eventually is correct is not such an
alien concept.

It is my humble opinion that mathematicians and logicians can learn to treat
truth with more malleability to allow for the formation of more formidable
domain tools.
\end{document}