\documentclass[12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{todonotes}

\author{Salvador Guzm\'{a}n}
\date{\today}
\title{Schemata for Effective Classroom Governance}
\hypersetup{
	pdfauthor={Salvador Guzm\'{a}n},
	pdftitle={Schemata for Effective Classroom Governance},
	pdfkeywords={},
	pdfsubject={},
	pdfcreator={},
	pdflang={English}
}

\begin{document}
	\maketitle
	\pagebreak
	\tableofcontents
	\pagebreak

	\section{Who Owns the Classroom?}
	\todo[inline, color=blue]{TODO}
	\subsection{Introduction}
	\todo[inline, color=blue]{TODO}
	\subsection{Thesis}
	\todo[inline, color=blue]{TODO}
	\subsection{The Current Classroom}
	\todo[inline, color=blue]{TODO}
	\subsection{The Restorative Approach}
	\todo[inline, color=blue]{TODO}
	
	\section{Current Classroom Circumstances}
	\todo[inline, color=blue]{TODO}
	\subsection{Trouble Students Controlling Class Climate}
	\todo[inline, color=blue]{TODO}
	\subsection{Insufficient institutional Pipeline to control discipline-challenged Students}
	\todo[inline, color=blue]{TODO}
	\subsection{Priority of Academic Performance at the Expense of Discipline}
	\todo[inline, color=blue]{TODO}
	\subsection{Opaque Management Decision Process}
	\todo[inline, color=blue]{TODO}
	\subsection{Disconnect Between Student-Centered Goals and Corporate Goals}
	\todo[inline, color=blue]{TODO}
	
	\section{The Restorative Approach, Dissected}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 1}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 2}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 3}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 4}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 5}
	\todo[inline, color=blue]{TODO}
	\subsection{Chapter 6}
	\todo[inline, color=blue]{TODO}

	\section{Questions that require an answer}
	\todo[inline, color=blue]{TODO}
	\subsection{Pedagogical Questions}
	\todo[inline, color=blue]{TODO}
	\subsubsection{What are the alternatives to this approach?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{What is the criteria for selection?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Is pedagogical counter-narratives allowed or addressed within the scope of the book?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Why was this specific approach chosen?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{What would it take to falsify the efficacy of this approach?}
	\todo[inline, color=blue]{TODO}
	\subsection{Efficacy Related Questions}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Has the restorative approach demonstrated success?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Has the restorative approach demonstrated failure?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{What is the track record of this approach?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does the restorative approach address classroom governance?}
	\todo[inline, color=blue]{TODO}
	\subsection{Tonal Questions}
	\todo[inline, color=blue]{TODO}
	\subsubsection{What was the intent of producing this piece of literature on this approach?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Who is the author?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does the author have a stake in the implementation of this approach?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{How does the author benefit from use of this approach?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does the tone allow any space for dissent?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does the tone address any criticism?}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Is intellectual criticism possible within the scope of the literature?}
	\todo[inline, color=blue]{TODO}
	
	\section{Attributes of a Successful Classroom}
	\todo[inline, color=blue]{TODO}
	\subsection{Positive Characteristics}
	\subsubsection{Teacher Morale}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Student Morale}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Classroom Ownership}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Classroom Social Dynamics}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Disciplinary Pipeline to Centralize Troublesome Students' Outbursts}
	\todo[inline, color=blue]{TODO}
	\subsection{Negative Characteristics}
	\subsubsection{Does not Offload Bulk Disciplinary Effort onto Teachers}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does not Designate Teachers as Head's of Discipline}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does not Force Teachers to Innovate to Achieve Disciplinary Ends}
	\todo[inline, color=blue]{TODO}
	\subsubsection{Does not See Teachers' Time as an Elastic Resource to be Tapped into}
	\todo[inline, color=blue]{TODO}
	
	\section{Conclusion}
	\todo[inline, color=blue]{TODO}
	
	
\end{document}